The Effect of Different Writing Tasks on Linguistic Style:\\ A Case Study of the ROC Story Cloze Task

### 2017-01-27 docs/language_constraint.tex
First complete draft

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2017}
\usepackage{times}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage[normalem]{ulem}
\usepackage{url}
\usepackage{pgfplots}
\usepackage{tikz}

@@

% Editing macros
\newcommand{\ms}[1]{{\color{cyan}\{\textit{#1}\}$_{ms}$}}
\newcommand{\roy}[1]{\footnote{\color{red}{\textbf{Roy: #1}}}}
\newcommand{\royb}[2]{{\color{red}{\sout{#1}}}{\color{green}{#2}}}
\newcommand{\royc}[3]{\royb{#1}{#2}\roy{#3}}

@@

\title{???}

@@

\begin{document}
\maketitle
\begin{abstract}
People's writing style is affected by many factors, including topics, sentiment, and individual personality. 
In this paper we show that writing tasks that impose constraints on the writer result in the author adopting a  different writing style compared to tasks that do not.
As a case study, we experiment with a recently published machine reading task: the story cloze task \cite{Mostafazadeh:2016}. 
In this task, annotators were asked to generate two sentences: one which makes sense given a previous paragraph and another which doesn't.
We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, obtains state-of-the-art results on the task,
substantially higher than sophisticated deep learning models.
Importantly, our model doesn't even look at the previous paragraph, just the two candidate sentences, which, out of context, differ only in the constraint put on the authors. 
Our results indicate that such constraints dramatically affect the way people write. 
They also suggest that careful attention to the instructions given to the authors needs to taken when designing new NLP tasks.

@@

\section{Introduction}
Writing style is defined as the the author's choice of words, spelling, grammar and punctuation.\footnote{\url{https://en.wikipedia.org/wiki/Writing_style}}
It is often affected by inter-writer factors such as age \cite{Schler:2006}, gender \cite{Argamon:2003}, native language \cite{Koppel:2005}, or mere personality \cite{Stamatatos:2009}, but also by other parameters such as the sentiment of the text \cite{Davidov:2010} and its level of sarcasm \cite{Tsur:2010}.  
In this paper we study to what extent is writing style affected by more intricate factors, such as the type of constraints put on the author.

As a testbed, we experiment with the story cloze task \cite{Mostafazadeh:2016}. 
In this task, authors were asked to write five-sentence self-contained stories.
Following, the stories were given to another group of authors, who were shown only the first four sentences of each story, 
and were asked to write two one-sentence endings for it: a {\it correct} ending, and a {\it wrong} ending.
The goal of the task is to determine which of the endings is the correct one.
\tabref{ROC-example} shows an example of an original story, a {\it correct} story and a {\it wrong} story.

\begin{table}[!t]
%\small
\begin{tabular}{|p{1.3cm}|p{5.6cm}|} \hline
{\bf Type} & {\bf Example} \\ \hline
{\it Original} story & My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	{\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
{\it Correct} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{forestgreen}{She felt buyer's remorse after the purchase.}} \\ \hline
{\it Wrong} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
\end{tabular}
\caption{\label{ROC-example}}
Examples of stories from the story cloze task. The first row shows an original story written by one author. 
The second and third row show two endings of the same story: a {\it correct} ending and a {\it wrong} one.
%\end{center}
\end{table}

@@

Our experiments indicate that the answer to both questions is positive. 
We train a linear classifier, using simple stylistic features, such as sentence length, character n-grams and PoS counts. 
First, we show that on a balanced dataset (random guess is 50\%) our classifier distinguishes between {\it correct} and {\it wrong} sentences in 64.5\% of the cases. 
Importantly, the classifier is trained {\bf only} on the last sentences, and does not consider the four input sentences.
%It is also trained on a set of positive samples and a set of negative ones, rather than pairs of (positive, negative) pairs, as in the original story cloze task.
Second, when trained to distinguish between original endings and new ({\it correct}) endings, the classifier obtains 70.9\% accuracy.

In order to estimate the quality of our results, we turn back to the story cloze task.
Using our classifier, we are able to obtain 71.5\% accuracy on the task, a 11.6\% improvement compared to the published state-of-the-art results \cite{Salle:2016}.\footnote{Recently, a shared task for the story cloze task has been published (\url{https://competitions.codalab.org/competitions/15333}). 
At the time of submission, the leading results is 71.1\%, which is much closer to our results, although still inferior.
No details about the methods used to generate this result are available.}
An ablation study shows that the style differences are realized in syntactic features (such as the over/under use of coordination words like ``and'' and ``but''),
but that sentiment also plays an important role in the writing style differences.
For instance, one of the key features for distinguishing between correct and wrong sentences is the over-representation of the word ``hate" in the latter.

@@

Our results may have a wide impact on a range of fields. 
First, they have the potential to shed light on cognitive processes that take place in the brain during writing.
Second, our results might have a more practical value in an era when fake news are becoming prominent,
as they suggest that these might have different style compared to real news.
Third, the results presented here also provide valuable lessons for designing new NLP tasks,
both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
%Although \cite{Mostafazadeh:2016} seem to have put a lot of effort into designing the task, 
%addressing many potential methodological flaws (see \secref{ROC_Story}), the importance of a few allegedly minor details were underestimated. 
%We show that these details are actually very significant.

Finally, one interesting question that remains open is whether state-of-the-art machine reading tools, for which this task was designed, 
capture in fact the same stylistic features as our linear classifier. 
We show that this is not the case. 
We train a neural language model on the original five sentence training corpus, and then compute the language probability of each of the candidates answers. 
We add the numbers as features in our linear classifier, and get an additional 3.6\% improvement (75.1\%).

The remainder of this paper is organized as follows. In \secref{ROC_Story} we introduce the cloze story task.
We present our model and our experiments at sections \ref{ssec:Model} and \ref{ssec:Experiments} respectively.
Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present an ablation study and a discussion, while \secref{Related}  surveys related work. 
We conclude at \secref{Conclusion}.

\isection{The Cloze Story Task}{ROC_Story}
%\roy{High level on first paragraph: much better, but still not enough connection to our story. You need to be explicit as to why we chose this task. Our work is currently not mentioned at all}
To understand how constrained writing affects writing style, we focus on the \textit{Story Cloze Task} \cite{Mostafazadeh:2016}. We exploit various interesting properties of the associated dataset and achieve state-of-the-art performance on the task.

Originally, the task was developed as an effort to facilitate representation and learning of commonsense knowledge. For that purpose, \citet{Mostafazadeh:2016} crowdsourced the collection of two types of datasets: the \textit{ROC Stories} and the \textit{Story Cloze test sets}.

\paragraph{ROC Stories}
consist of $98,163$ % \roy{Minor, but still: writing the number inside dollar signs adds a white space in the pdf. This is a bit annoying, and also potentially confusing, as in the next case you use it below (3,744 something)}
five-sentence commonsense stories, collected on Amazon Mechanical Turk (AMT). Workers were instructed to write a coherent story where something happens, and with%\roy{``and with'' doesn't sound right here. rephrase}
a clear beginning and end. To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories.
\paragraph{Story Cloze}%\roy{say something general first before diving into details} 
test sets consist of $3,744$ short stories, each with one ``right'' and one ``wrong'' ending, also collected on AMT.
Presented with the first four sentences of a ROC story, workers were asked to write a ``right'' and a ``wrong'' ending. Both endings had to complete the story using one of the characters in it, and when read out of context, the ending had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.

The resulting stories, matched with each ending, were then individually rated for coherence and meaningfulness by AMT workers. Only stories rated as simultaneaously coherent with a ``right'' ending and neutral with a ``wrong'' ending were selected for the test. It is worth noting that workers rated the stories as a whole, not the endings; no selection was done on the endings alone.

\paragraph{Design.}
In this task, training (ROC Stories) and test (Story Cloze) data were created differently.
%The task was designed such that the ROC stories would be used as training data and the Story Cloze stories as validation and test sets, i.e. the training and test data were created differently. 
The ROC Stories were written by one author, and only have one ``right'' ending, whereas the Story Cloze stories have two endings, neither or which were written by the author of the rest of the story. Furthermore, \citet{Mostafazadeh:2016} made sure the Story Cloze endings would be hard to distinguish automatically, as each pair of endings was written by the same author. We show that, as a result of these design choices, the style of the ROC stories is rather different from the Story Cloze stories.

\paragraph{Benchmarks.} While the Story Cloze test is now the LSDSem `17 Shared Task and was proposed as a testbed for vector-space evaluation \cite{mostafazadeh2016story}, reported performance isn't far from a random baseline. \citet{Mostafazadeh:2016} implemented various benchmarks trained on the ROC Stories, using surface level features as well as narrative-informed ones. Compared to similar tasks \cite{hermann2015teaching,rajpurkar2016squad,bowman2015large}, the benchmarks perform relatively poorly, indicating that high performance is hard to achieve.
To the best of our knowledge, no training has been done on pairs of endings.

@@

We train a linear SVM classifier to distinguish between different endings. 
Each feature vector is computed using the words in one ending, without considering earlier parts of the story. 
We use the following style features.

\begin{itemize}
\item\textit{\textbf{Length~}} The number of words in the sentence.
\item\textit{\textbf{Word n-grams~}} We use sequences of 1-5 words. Following \cite{Tsur:2010,Schwartz:2013}, we distinguish between high frequency and low frequency words. 
Specifically, we replace content words with their part-of-speech tags (Nouns, Verbs, Adjectives and Adverbs).
\item\textit{\textbf{Character n-grams~}} Character n-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
We used character 5-grams.
\end{itemize}

\isectionb{Experiments}
We design two experiments to answer our research questions. 
The first is an attempt to distinguish between {\it correct} and {\it wrong} endings.
The second attempts to distinguish between original endings and new {\it correct} endings.
We describe both experiments below.

\paragraph{Experiment 1: Correct/Wrong Endings.}
The goal of this experiment is to measure to what extent  style features capture differences between {\it correct} and {\it wrong} endings.
As the cloze story task doesn't have a training corpus for the {\it correct} and {\it wrong} endings, we use the development set as our training set. 
We split it (90/10) into our training and development set. We keep the story cloze test set as is.
The final size of our training/development/test sizes are 3366/374/3742, respectively.

We take  {\it correct} endings as positive samples and {\it wrong} endings as our negative examples. 
By ignoring the coupling between {\it correct}/{\it wrong} pairs, we are able make a more general claim about the style used when writing each of the tasks.

We add a special START symbol at the beginning of each sentence. 
For computing our features, we keep n-gram (character or word) features that occur at least five times in the training set.\footnote{Virtually all sentences end with a period, so no need for an END token}
For the PoS features, we tag each sentence with the Spacy PoS tagger.\footnote{\url{spacy.io/}}
We use  sklearn's LinearSVC SVM implementation\footnote{\url{scikit-learn.org/stable/modules/generated/sklearn.svm.LinearSVC.html}} 
with L2 loss. We grid search the regularization parameter on our development set.

@@

Here the goal is to measure whether writing the ending as part of a story imposes different style compared to writing a ({\it correct}) ending to an existing story.
We use the endings of the original ROC stories as our {\it original} training samples and {\it correct} endings from the ROC stories development set as {\it new} training samples.
As there are far more {\it original} samples than {\it new} ones, we randomly select $N$ {\it original} samples, where $N$ is the number of {\it new} samples,
such that we have balanced labels in our training, validation and test sets.
We apply the same experimental decisions as in Experiment 1, and repeat this process 5 times while reporting the average.

\paragraph{Results.}
\figref{results} shows our results.
Results show that for Experiment 1, our model obtains results well above a random baseline -- 64.5\% classification accuracy. 
For Experiment 2, we get even higher results -- 70.9\%. 
These numbers indicate that these different writing tasks clearly impose a different writing style on authors.

As a complementary experiment, we measured whether these style differences are additive. 
That is, whether the style differences between {\it correct} endings and {\it wrong} ones are different from the differences between {\it correct} and {\it original} endings.
We repeated Experiment 2, this time comparing between {\it original} and {\it wrong} sentences. 
Our hypothesis is that differences would be even clearer. 
Our results (\figref{results}) show that this is indeed the case: the classifier's accuracy jumps to 78\%.

@@

        \addplot[style={rred,fill=rred,mark=none}]
            coordinates {({\it Correct/Wrong}, 0.645) ({\it Original/New}, 0.709) ({\it Original/Wrong},0.78)};

        \legend{Random Baseline, Our Model}
    \end{axis}
\end{tikzpicture}
\caption{\label{results} Results of  experiments 1 and 2 (left two charts). 
Rightmost experiment shows a control experiment which classifies {\it original} endings vs \textit{\textbf{wrong}} endings. }
\end{figure}

\paragraph{Story Cloze.}
Results of Experiment 1 indicate that {\it correct} and {\it wrong} endings are characterized by different styles.
In order to estimate the quality of our classification results, we tackle the story cloze task using our classifier.
This classification task is much more constrained than Experiment 1, as here the task is given two endings, which one is {\it correct} and which is {\it wrong}.
In order to solve the task, we use the output of our trained classifier. 
For each pair of endings $e_1,e_2$, if both endings have different classification labels, we keep these labels. 
If they share the same label, we use the classifier confidence level as a deciding factor: the label of the one with the lower confidence is reversed.

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2017}
\usepackage{times}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage[normalem]{ulem}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{pgfplots}
\usepackage{tikz}

@@

% Editing macros
\newcommand{\my}[1]{\footnote{\color{red}{\textbf{#1}}}}

\newcommand{\ms}[1]{{\color{cyan}\{\textit{#1}\}$_{ms}$}}
\newcommand{\roy}[1]{\footnote{\color{red}{\textbf{Roy: #1}}}}
\newcommand{\royb}[2]{{\color{red}{\sout{#1}}}{\color{green}{#2}}}
\newcommand{\royc}[3]{\royb{#1}{#2}\roy{#3}}

@@

\title{The Effect of Different Writing Tasks on Linguistic Style:\\ A Case Study of the ROC Story Cloze Task}

@@

\begin{document}
\maketitle
\begin{abstract}
People's writing style is affected by many factors, including topics, sentiment, and individual personality. 
In this paper we show that engaging authors in different  writing tasks results in them adopting different writing styles.
As a case study, we experiment with a recently published machine reading task: the {\it Story Cloze task} \cite{Mostafazadeh:2016}. 
In this task, annotators were asked to generate two sentences: one which makes sense given a previous paragraph and another which doesn't.
We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, obtains state-of-the-art results on the task,
substantially higher than sophisticated deep learning models.
Importantly, our model doesn't even look at the previous paragraph, just the two candidate sentences, which, out of context, differ only in the writing task presented to the authors. 
Our results indicate that different tasks dramatically affect the way people write. 
They also provide important lessons for designing new NLP tasks.

@@

\section{Introduction}
Writing style is defined as the the author's choice of words, spelling, grammar and punctuation.\footnote{\url{https://en.wikipedia.org/wiki/Writing_style}}
It is often affected by inter-writer factors such as age \cite{Schler:2006}, gender \cite{Argamon:2003} or mere personality \cite{Stamatatos:2009}, but also by other parameters such as the sentiment of the text \cite{Davidov:2010}, its level of sarcasm \cite{Tsur:2010} and whether it's deceptive \cite{Feng:2012}.  
In this paper we study to what extent is writing style affected by more intricate factors, such as the nature of the writing task.

\begin{table}[!t]
%\small
\begin{tabular}{|p{1.3cm}|p{5.6cm}|} \hline
{\bf Type} & {\bf Example} \\ \hline
{\color{blue}{\it Original}} story & My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	{\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
{\color{forestgreen}{\it Correct}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{forestgreen}{She felt buyer's remorse after the purchase.}} \\ \hline
{\color{red}{\it Wrong}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
\end{tabular}
\caption{\label{ROC-example}}
Examples of stories from the story cloze task. The first row shows an {\it original} story written by one author. 
The second and third row show two endings of the same story: a {\it correct} ending and a {\it wrong} one.
%\end{center}
\end{table}

As a testbed, we experiment with the story cloze task \cite{Mostafazadeh:2016}. 
In this task, authors were asked to write five-sentence self-contained stories (henceforth {\it original} stories).
Following, the stories were given to other authors, who were shown only the first four sentences of each story, 
and were asked to write two one-sentence endings: a {\it correct} ending, and a {\it wrong} ending.
The goal of the task is to determine which of the endings is the correct one.
\tabref{ROC-example} shows an example of an {\it original} story, a {\it correct} story and a {\it wrong} story.

@@

Our experiments indicate that the answer to both questions is positive. 
We train a linear classifier, using simple stylistic features, such as sentence length, character n-grams and word n-grams. 
First, we show that on a balanced dataset (chance level is 50\%) our classifier distinguishes between {\it correct} and {\it wrong} endings in 64.5\% of the cases. 
%It is also trained on a set of positive samples and a set of negative ones, rather than pairs of (positive, negative) pairs, as in the original story cloze task.
Second, when trained to distinguish between {\it original} endings and new ({\it correct}) endings, the classifier obtains 68.5\% accuracy. 
Importantly, in both experiments, the classifier uses {\bf only} the last sentence of each of the stories, and does not consider the first four sentences.

In order to further estimate the quality of our results, we turn back to the story cloze task.
Adapting our classifier to the task, we obtain 72.4\% accuracy, a 12.5\% improvement compared to the published state-of-the-art results \cite{Salle:2016}.\footnote{Recently, a shared task for the story cloze task has been published (\url{https://competitions.codalab.org/competitions/15333}). 
At the time of submission, the leading results was 71.1\%, which is  closer to our results, although still inferior.
No details about the validity of this result or the methods used to generate it are available.}
When analyzing the results of our classifier, we see that sentiment plays a significant role in its success,
which suggests that constraining authors to ``wrong'' sentences results in negative text.

We show that the style differences captured by our model can be combined with a state-of-the-art machine reading tool, for which this task was designed, in order to get increased performance on the story cloze task.  
We train a neural language model on the {\it original} five sentence training corpus, and then compute the language probability of each of the candidate endings. 
We add the resulting probabilities as features in our linear classifier, and get an additional 2.8\% improvement -- 75.2\% -- which is 15.3\% better than the best published result.
%For instance, one of the key features for distinguishing between correct and wrong sentences is the over-representation of the word ``hate" in the latter.

@@

Our results may have a wide impact on a range of fields. 
First, they have the potential to shed light on cognitive processes that take place in the brain during writing.
%Second, our results might have a more practical value in an era when fake news are becoming prominent,
%as they suggest that these might have different style compared to real news.
Second, the results presented here also provide valuable lessons for designing new NLP tasks,
both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
%Although \cite{Mostafazadeh:2016} seem to have put a lot of effort into designing the task, 
%addressing many potential methodological flaws (see \secref{ROC_Story}), the importance of a few allegedly minor details were underestimated. 
%We show that these details are actually very significant.

The remainder of this paper is organized as follows. In \secref{ROC_Story} we introduce the cloze story task.
We present our model, our experiments and our resutls in sections \ref{ssec:Model}, \ref{ssec:Experiments} and \ref{ssec:Results} respectively.
Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present an ablation study and a discussion, while \secref{Related}  surveys related work. 
We conclude at \secref{Conclusion}.

\isection{The Cloze Story Task}{ROC_Story}
In this paper, we seek to understand how different writing tasks affect writing style.
To do so, we focus on the \textit{Story Cloze Task} \cite{Mostafazadeh:2016}. 
While this task was developed to facilitate representation and learning of commonsense knowledge,
it introduces a few interesting properties which makes it ideal for our purpose. 
We describe the task below.

%For that purpose, \citet{Mostafazadeh:2016} crowdsourced the collection of two types of datasets: the \textit{ROC Stories} and the \textit{Story Cloze test sets}.

\paragraph{ROC Stories.}

The ROC Story Corpus consists of 49,255 five-sentence commonsense stories, collected on Amazon Mechanical Turk (AMT).\footnote{Recently, an additional 53K stories were released, which results in roughly 100K stories.}
Workers were instructed to write a coherent story, which has a clear beginning and end. 
To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories,
which resulted in a wide range of different topics.

\paragraph{Story Cloze Task.}
After compiling the story corpus, the {\it Story Cloze Task} -- a task based on the corpus -- was introduced.
A subset of the stories was selected, and the first four sentences of each story were presented to AMT workers.
Workers were asked to write a {\it correct} and a {\it wrong} ending to each story prefix. 
Both endings had to complete the story using one of the characters in it.
Importantly,  when read out of context, the ending had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.

The resulting stories, both {\it correct} and {\it wrong}, were then individually rated for coherence and meaningfulness. 
Only stories rated as simultaneously coherent with a {\it correct} ending and neutral with a {\it wrong} ending were selected for the task. 
It is worth noting that workers rated the stories as a whole, not only the endings.

Based on the new stories, \citet{Mostafazadeh:2016} proposed the {\it Story Cloze Task}. 
The task is simple -- given a pair of stories that differ only in their endings, the system is required to determine which ending is {\it correct} and which is {\it wrong}.
The authors published the ROC story corpus as the training data, and the task composed of development and test sets for which both {\it correct} and {\it wrong} endings are found.
The task was suggested as an extensive evaluation framework:
as a machine reading task, as the shared task for the  Linking Models of Lexical, Sentential and Discourse-level Semantics workshop (LSDSem 2017), and as a testbed for vector-space evaluation \cite{mostafazadeh2016story}.

\paragraph{State-of-the-Art Performance.}
Interestingly, at the time of submission, 10 months after the paper was first published, the published benchmark on this task is still below 60\% \cite{Salle:2016}.\footnote{The LSDSem`17 shared task website does report higher results (71.1\%), which are still unpublished.}
This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SQuAD \cite{rajpurkar2016squad} and SNLI \cite{bowman2015large}, for which results improved dramatically over a similar period of time.
This suggest that this task is challenging and that high performance is hard to achieve.

\paragraph{Different Writing Tasks in the Story Cloze Task.}
\citet{Mostafazadeh:2016} made substantial efforts to ensure the quality of this task. 
First, each pair of endings was written by the same author, which ensured that author style differences could not be used to solve the task. 
Furthermore, the authors implemented nine baselines for the task, using surface level features as well as narrative-informed ones, and showed that each of them reached roughly chance-level.
These results indicate that real understanding of text is required in order to solve the task.

Despite these efforts, several key aspects were not controlled for. 
First, the training set for the task (ROC Stories corpus) is not really a training set, as it contains only positive ({\it correct}) samples, and not negative ({\it wrong}) ones. 
On top of that, the {\it original} endings, which serve as positive training samples, were generated differently from the {\it correct} samples, which serve as the positive samples in the development and test sets. 
While the former are part of a single coherent story written by the same author, the latter were generated by letting an author read four sentences, 
and then asking her to generate a fifth {\it correct} ending. 
This raises the question of whether these different writing setups impose different writing styles. 
We show that this is indeed the case.

Second, although the {\it correct} and {\it wrong} sentences were generated by the same author, 
the tasks for generating them were quite different: in one case, the author was asked to write a {\it correct} ending, which would create a coherent five-sentence story along with the other four sentences. In the other case, the author was asked to write a {\it wrong} ending, which would result in an incoherent five-sentence story. 
In this work, we show that these differences are significant and impose different writing styles on authors.

\paragraph{Initial Analysis.}
We computed several characteristics of the three types of endings: {\it original} endings (from the ROC Story Corpus training set), {\it correct} endings and {\it wrong} endings (both from the story cloze task development set).
Our analysis  reveals several style differences between the different groups. 
First, {\it original} endings are on average much longer (11 words per sentence) than {\it correct} endings (8.75 words), which are in turn also longer (though not as much)  than {\it wrong} ones (8.47 words).
Second, \figref{roc_pos_distribution} shows the distribution of five frequent PoS tags in all three groups. 
The figure shows that both {\it original} and {\it correct} endings use pronouns more frequently than {\it wrong} endings,
which in turn prefer proper nouns, especially compared to {\it original} endings.

Finally, \figref{roc_word_distribution} presents the distribution of five frequent words across the different groups. 
The figure shows that {\it original} endings prefer to use coordinations (``and'') more than  {\it correct} endings, and substantially more than {\it wrong} ones.
Furthermore, {\it original} and {\it correct} endings seem to prefer positive words (e.g., ``better''), while {\it wrong} endings prefer negative ones (``hates'').
Next we show that these style differences are not anecdotic, but can be used to distinguish between the different groups of text.

\com{\begin{table*}[!t]
\begin{center}
%\small
\begin{tabular}{|p{2.5cm}|p{4cm}|p{4cm}|p{4cm}|} \hline
 & {\bf Original}& {\bf Correct} & {\bf Wrong}\\ \hline
Sentence Length (\#words) & 11.02 & 8.75 & 8.47\\ \hline
Most Frequent PoS tags (\%)  & NN:15.3\%, VBD:13.4\%, PRP:10.1, DT:9.1\%, IN:8.7\% & VBD:15.8\%, NN:15.7\%, DT:9.7\%, PRP:8.8\%, NNP:8.3\%  & NN:16.3\%, VBD:15.1\%,  NNP:9.5\%, DT:9.4, IN:7.9\%\\ \hline
Most Frequent Words  (\%) & the:4.5\%, to:3.3\%, and:2.7\%, was:2.6\%, a:2.2\% & the:4.8\%, to:3.9\%, was:3.5\%, a:2.5\%, and:2.1\%   & the:5\%, to:4\%, was:3\%, a:2\%, I:1.6\%\\ \hline
\end{tabular}
\end{center}
\caption{\label{roc_pos_distribution} 
\end{table*}
}}

\begin{figure*}[t!]
\begin{subfigure}{.5\textwidth}
\begin{tikzpicture}
\small
    \begin{axis}[
        width  = 0.4*\textwidth,
        height = 4cm,
      %  major x tick style = transparent,
        ybar=\pgflinewidth,
        x=2.5cm,
       bar width=5pt,
        ymajorgrids = true,
        ylabel = {Frequency in Corpus (\%)},
        symbolic x coords={{\it Original}, {\it Correct}, {\it Wrong}},
        xtick = data,
        scaled y ticks = false,
        %enlarge x limits=0.25,
        ymin=3,
        legend cell align=left,
        legend style={
        		legend columns=-1,
                at={(1,1.05)},
                anchor=south east,
                column sep=1ex
        }
    ]
        \addplot[style={bblue,fill=bblue,mark=none}]
            coordinates {({\it Original}, 15.3) ({\it Correct}, 15.7) ({\it Wrong}, 16.3)};

        \addplot[style={rred,fill=rred,mark=none}]
            coordinates {({\it Original}, 13.4) ({\it Correct}, 15.8) ({\it Wrong}, 15.1)};

        \addplot[style={ggreen,fill=ggreen,mark=none}]
            coordinates {({\it Original}, 10.1) ({\it Correct}, 9.7) ({\it Wrong}, 7.4)};

        \addplot[style={brown,fill=brown,mark=none}]
            coordinates {({\it Original}, 9.1) ({\it Correct}, 9.7) ({\it Wrong}, 9.4)};

        \addplot[style={gray,fill=gray,mark=none}]
            coordinates {({\it Original}, 4.7) ({\it Correct}, 8.3) ({\it Wrong}, 9.5)};

        \legend{NN, VBD, PRP, DT, NNP}
    \end{axis}
\end{tikzpicture}
\caption{\label{roc_pos_distribution}PoS tags}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
\begin{tikzpicture}
\small
    \begin{axis}[
        width  = 0.4*\textwidth,
        height = 4cm,
      %  major x tick style = transparent,
        ybar=\pgflinewidth,
        x=2.5cm,
       bar width=5pt,
        ymajorgrids = true,
%        ylabel = {Frequency in Corpus (\%)},
        symbolic x coords={{\it Original}, {\it Correct}, {\it Wrong}},
        xtick = data,
        scaled y ticks = false,
        %enlarge x limits=0.25,
        ymin=0,
        legend cell align=left,
        legend style={
        		legend columns=-1,
                at={(1,1.05)},
                anchor=south east,
                column sep=1ex
        }
    ]
        \addplot[style={bblue,fill=bblue,mark=none}]
            coordinates {({\it Original}, 3.4) ({\it Correct}, 3.9) ({\it Wrong}, 4)};

        \addplot[style={rred,fill=rred,mark=none}]
            coordinates {({\it Original}, 2.8) ({\it Correct}, 2) ({\it Wrong}, 1.5)};

        \addplot[style={ggreen,fill=ggreen,mark=none}]
            coordinates {({\it Original}, 1.1) ({\it Correct}, 1.4) ({\it Wrong}, 1.6)};

        \addplot[style={brown,fill=brown,mark=none}]
            coordinates {({\it Original}, 0) ({\it Correct}, 0) ({\it Wrong}, 0.7)};

        \addplot[style={gray,fill=gray,mark=none}]
            coordinates {({\it Original}, 0.1) ({\it Correct}, 0.2) ({\it Wrong}, 0)};

        \legend{to, and, I, hates, better}
    \end{axis}
\end{tikzpicture}
\caption{\label{roc_word_distribution}Words}
\end{subfigure}
\caption{The distribution of five frequent PoS tags (\ref{roc_pos_distribution}) and words (\ref{roc_word_distribution})  across different endings: {\it Original} -- endings of stories from the ROC story corpus (the story cloze training set). {\it Correct} -- correct endings, {\it Wrong} -- wrong endings (both from story cloze task).}

\end{figure*}

@@

We train a linear logistic regression (aka Maximum Entropy) classifier to distinguish between different endings. 
Each feature vector is computed using the words in one ending, without considering earlier parts of the story. 
We use the following style features.

\begin{itemize}
\item\textit{\textbf{Length}.} The number of words in the sentence.
\item\textit{\textbf{Word n-grams.}} We use sequences of 1-5 words. Following \cite{Tsur:2010,Schwartz:2013}, we distinguish between high frequency and low frequency words. 
Specifically, we replace content words, which are often low frequency, with their part-of-speech tags (Nouns, Verbs, Adjectives and Adverbs).
\item\textit{\textbf{Character n-grams.}} Character n-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
We use character 4-grams.
\end{itemize}

\isectionb{Experiments}
We design two experiments to answer our research questions. 
The first is an attempt to distinguish between {\it correct} and {\it wrong} endings.
The second attempts to distinguish between {\it original} endings and new ({\it correct}) endings.
We describe both experiments below.

\paragraph{Experiment 1: Correct/Wrong Endings.}
The goal of this experiment is to measure to what extent  style features capture differences between {\it correct} and {\it wrong} endings.
As the cloze story task doesn't have a training corpus for the {\it correct} and {\it wrong} endings (see \secref{ROC_Story}), we use the development set as our training set. 
We split it (90/10) into our training and development set. We keep the story cloze test set as is.
The final size of our training/development/test sizes are 3,366/374/3,742 endings, respectively.

It is worth nothing that our classification task is slightly different from the {\it story cloze Task}. 
Instead of classifying pairs of endings, one which is {\it correct} and another which is {\it wrong}, we take the set of  {\it correct} endings as positive samples and the set of {\it wrong} endings as our negative examples. 
By ignoring the coupling between {\it correct} and {\it wrong} pairs, we are able make a more general claim about the style used when writing each of the tasks.

@@

Here the goal is to measure whether writing the ending as part of a story imposes different style compared to writing a ({\it correct}) ending to an existing story.
We use the endings of the ROC stories as our {\it original} training samples and {\it correct} endings from the story cloze task  development and test sets as {\it new} training samples.
As there are far more {\it original} samples than {\it new} ones, we randomly select $N$ {\it original} samples, where $N$ is the number of {\it new} samples,
such that we have balanced labels in our training, validation and test sets (sizes are the same as in Experiment 1).
We randomly sample 5 training sets and report the average classification result.

\paragraph{Experimental Setup.}
In both experiments, we add a START symbol at the beginning of each sentence.\footnote{Virtually all sentences end with a period or an exclamation mark, so we do not add an END token} 
For computing our features, we keep n-gram (character or word) features that occur at least five times in the training set.
All feature values are normalized to [0-1].
For the PoS features, we tag all endings with the Spacy PoS tagger.\footnote{\url{spacy.io/}}
We use  python's sklearn logistic regression implementation with L2 loss. 
We grid search the regularization parameter on our development set.

\isectionb{Results}
\figref{results} shows our results.
Results show that for Experiment 1, our model obtains results well above a random baseline -- 64.5\% classification accuracy. 
For Experiment 2, we get even higher results -- 68.5\%. 
These numbers indicate that these different writing tasks clearly impose different writing styles on authors.

As a complementary experiment, we measured whether these style differences are additive. 
That is, whether the style differences between {\it correct} endings and {\it wrong} ones are different from the differences between {\it correct} and {\it original} endings.
We repeated Experiment 2, this time comparing between {\it original} and {\it wrong} sentences. 
Our hypothesis is that differences would be even clearer. 
Our results (\figref{results}) show that this is indeed the case: the classifier's accuracy jumps to 75.2\%.

@@

        \addplot[style={rred,fill=rred,mark=none}]
            coordinates {({\it Correct/Wrong}, 0.645) ({\it Original/New}, 0.685) ({\it Original/Wrong},0.756)};

        \legend{Random Baseline, Our Model}
    \end{axis}
\end{tikzpicture}
\caption{\label{results} Results of  experiments 1 and 2 (left two charts). 
Rightmost graph shows a control experiment which classifies {\it original} endings vs \textit{\textbf{wrong}} endings. }
\end{figure}

\paragraph{Story Cloze Task.}
The results of Experiment 1 indicate that {\it correct} and {\it wrong} endings are characterized by different styles.
In order to further estimate the quality of our classification results, we tackle the story cloze task using our classifier.
This classification task is more constrained than Experiment 1, as here the task is given two endings, which one is {\it correct} and which is {\it wrong}.
In order to solve the task, we use the output of our trained classifier. 
For each pair of endings in our test set, if the classifier assigns different labels to them, we keep these labels. 
If they share the same label, then one of them must be wrong, so we use the classifier confidence level as a deciding factor: the label of the one with the lower confidence is reversed.

\tabref{cloze_results} shows our results on the story cloze test set. Our classifier obtains 72.4\% accuracy, which is 12.5\% higher than the published state-of-the-art result on the task.
Importantly, unlike previous approaches, our classifier does not require the story corpus training data, and in fact doesn't even look at the first four sentences of the story in question.
These numbers indicate that the styles of {\it correct} and {\it wrong} endings are indeed very different.
